The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-05 paper/main.tex
Added more sources and some research questions.

\emph{Hypothesis 3: There will be more Issue Reporters than Committers by an order of magnitude.}\\
Research into the Apache Server project observed that there were far more \emph{Issue Reporters} than there were code \emph{Committers}\cite{mockus2000case}. The Apache Server project is an excellent case study in this type of Developer Hierarchy. Apache is built around a small set of {\it Core Developers}, followed by {\it Defect Repairers} and {\it Defect Reporters}. Each level of this hierarchy brings with it an order of magnitude increase in number of participants. The 10-15 {\it Core Developers} contribute around 80\% of the new functionality, while the rest of the 400 code contributors focus primarily on bug fixes. The {\it Defect Reporters} were by far the largest group, with over 3000 individuals submitting bug reports.\\

Because issue reporting is of low risk to the code base, but has potentially high value, it is a perfect way for large numbers of people to contribute. It is expected that the findings of the Apache Server project research will hold true for GitHub projects as well.

@@

\section{Results}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/issue_close_time_forks_scatterplot.png}

\emph{Hypothesis 2: As the number Repository Forks increase, the Issue Resolution Time will decrease.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}

@@

>>>>

\emph{Hypothesis 3: There will be more Issue Reporters than Committers by an order of magnitude, but the number of Committers will remain small.}\\
Research into the Apache Server project observed that there were far more \emph{Issue Reporters} than there were code \emph{Committers}\cite{mockus2000case}. The Apache Server project is an excellent case study in this type of Developer Hierarchy. Apache is built around a small set of {\it Core Developers}, followed by {\it Defect Repairers} and {\it Defect Reporters}. Each level of this hierarchy brings with it an order of magnitude increase in number of participants. The 10-15 {\it Core Developers} contribute around 80\% of the new functionality, while the rest of the 400 code contributors focus primarily on bug fixes. The {\it Defect Reporters} were by far the largest group, with over 3000 individuals submitting bug reports.\\

Because issue reporting is of low risk to the code base, but has potentially high value, it is a perfect way for large numbers of people to contribute. It is expected that the findings of the Apache Server project research will hold true for GitHub projects as well.\\

\subsection{Research Questions}

\emph{Research Question 1: There will be more Issue Reporters than Committers by an order of magnitude, but the number of Committers will remain small.}\\
A smal core of developers, however, seems to be a historial fact of OSS development\cite{mockus2000case,mockus2000two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changes this?

\emph{Research Question 2: What is the GitHub Philosophy?}\\
The socal aspects of GitHub are an important part of the experience\cite{dabbish2012social}. User interactions and social pressures can drive OSS development in interesting ways. Social aspects of OSS development have existed before GitHub, with mailing lists\cite{mockus2000case}, gift giving mechanisms\cite{bergquist2008power}, and other code hosting sites. What is GitHub doing to facilitate change on OSS development, and how does it see OSS development changing moving forward?

@@

\section{Results}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}

\emph{Hypothesis 2: As the number Repository Forks increase, the Issue Resolution Time will decrease.}\\
\includegraphics[height=3in,width=3in]{images/issue_close_time_forks_scatterplot.png}

@@

\subsection{Other Findings}
\emph{The Git SCM }\\

\emph{The GitHub Process applies to more than code artifacts}\\
